---
title: "HW 2 Student"
author: "Andy Ackerman"
date: "10/17/2023"
output: 
  html_document:
    number_sections: true
---

This homework is meant to illustrate the methods of classification algorithms as well as their potential pitfalls.  In class, we demonstrated K-Nearest-Neighbors using the `iris` dataset.  Today I will give you a different subset of this same data, and you will train a KNN classifier.  

```{r, echo = FALSE}
set.seed(123)
library(class)

df <- data(iris) 

normal <-function(x) {
  (x -min(x))/(max(x)-min(x))   
}

iris_norm <- as.data.frame(lapply(iris[,c(1,2,3,4)], normal))

subset <- c(1:45, 58, 60:70, 82, 94, 110:150)
iris_train <- iris_norm[subset,] 
iris_test <- iris_norm[-subset,] 

iris_target_category <- iris[subset,5]
iris_test_category <- iris[-subset,5]
```

#
Above, I have given you a training-testing partition.  Train the KNN with $K = 5$ on the training data and use this to classify the 50 test observations.  Once you have classified the test observations, create a contingency table -- like we did in class -- to evaluate which observations your algorithm is misclassifying.   

```{r}
pr <- knn(iris_train,iris_test,cl=iris_target_category,k=5)
tab <-table(pr, iris_test_category)
tab

```

```{r}
accuracy <- function(x){
  sum(diag(x)/(sum(rowSums(x)))) * 100
}
accuracy(tab)
```







#

Discuss your results.  If you have done this correctly, you should have a classification error rate that is roughly 20% higher than what we observed in class.  Why is this the case? In particular run a summary of the `iris_test_category` as well as `iris_target_category` and discuss how this plays a role in your answer.  

*STUDENT INPUT* 
```{r}
summary(iris_test_category)
summary(iris_target_category)
```
```

The test and training categories seem to be not sampled randomly.  versicolor is much more present in the test data than the training data.  Because of this there are a lot of versicolor being tested that come back from the tests virginica; because there are not a representative amount of virginica in the training and test data.  

Choice of $K$ can also influence this classifier.  Why would choosing $K = 6$ not be advisable for this data? 

*STUDENT INPUT*

# Choosing K = 6 would not make much sense because then you can have an instance where you essentially have a "tie".  This is not good because then R just picks which side to classify it as and this is not as good as making it the 5 nearest or 7 nearest.

Build a github repository to store your homework assignments.  Share the link in this file.  

*STUDENT INPUT*

